Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma

### 2021-06-07 Cover_letter_JPM.tex
Updates from Overleaf
Answer 2-1 done (FDR)

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{degs}{DEGs}{differentially expressed genes}

@@

\subsection*{1-1}
%\begin{MyColorPar}{blue}
First of all, please describe the difference between the two manuscripts.

@@

We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

@@

\subsection*{1-2}
\label{page:1-2}
%
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

@@

After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

@@

The authors introduced a workflow to identify gene-expression biomarkers based on TCGA data and applied it to head and neck squamous cell carcinoma. The authors tried to highlight their workflow and present it as a new tool, however, their workflow is very common, and I cannot see its novelty. 
The selection of gene expression cutoff is not well handled statistically (see below my first comment). 
Therefore, I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone
Exploring all possible expression cutoffs is also usable but should only be used for established biomarkers. Once it is known that a gene is a strong biomarker (e.g., from a genome-wide test using fixed cutoffs), one can fine-tune the cutoffs utilizing this strategy.

\subsection*{2-1}

Exploring all possible expression cutoffs is controversial. A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.

We appreciate the reviewer for kind instruction of expression cutoff in detail.\\
***We modified the workflow as ...

We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

\begin{MyColorPar}{red}
The \acrfull{fdr} ($< 0.05$) correction has been applied to ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
\end{MyColorPar}

@@

\subsection*{2-2}

I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

@@

We appreciate the reviewer for the critical comment.
We changed title as "Transcriptomic Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.

* more evidence to support or validate them

\subsection*{2-3}

% strategy should changing; run GCP Rstudio? hard work to do
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. The p-values are affected by the sample size, which should be described in the main text. As I mentioned above, the authors should look for more data to verify these biomarkers.

We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
***調整 workflow 更加嚴格以增加 validation rate
Validation rate: 
FDR for Cutoff mining: 先偷看答案 2837
重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837)

@@

Validation by:
TCIA CPTAC (not HPA 抗體很少）

This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.

https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
As digital tissue microarray?

===
For validation by GEO datasets:
*The p-values are affected by the sample size, which has be described in the main text.

GEOquery: SOFT file (or MINiML) %https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
*the authors should look for more data to verify these biomarkers.
by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
or CPTAC (digital TMA, not HPA)i

or more GEO datasets (GEO2837, GSE40774, GSE65858, GSE148944, and GSE41613/xGSE42743)i
**  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
*** \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
GEO2R: GSE41613 and GSE42743 has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
from 97 HPV-negative OSCC patients %on the 131 gene 
to identify a model for prediction of OSCC-specific survival\cite{Lohavanichbutr2013}.

as following: % search by StarGEO
StarGEO http://stargeo.org/ searching: HNSCC + survival (n>100]
GSE 2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837

and more
https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
n=134; Agilent-026652 Whole Human Genome Microarray 4x44K v2 (Probe Name version)
supplementary data:
https://clincancerres.aacrjournals.org/content/21/4/870.figures-only#fig-data-additional-files
# Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma getGEO("GSE40774", GSEMatrix =TRUE, cex=1.5)library("maptools")

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858GSE65858
https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649

https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
   784 probes (gene）
n=40; 110 FFPE samples were collected from a retrospective cohort of 67 OTSCC patients and 10 non-cancerous tongue samples. Targets including CD4, CD8, FOXP3, PD-L1 and PD-1 were analyzed by immunohistochemistry. The Nanostring PanCancer Immune Profiling Panel was used for gene expression profiling. Data were externally validated in the TCGA head and neck (HNSCC), melanoma and lung squamous cell carcinoma (LSCC) cohorts.
GPL28285
NanoString nCounter PanCancer Immune Profiling Panel

@@

% *** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.

% #####################
\subsection*{2-4} % (ok)

How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?

We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

@@

\subsection*{2-6}
\subsubsection*{[Minor comments]}
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

% (ok) minor comments1
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]

@@

Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{p} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{p} value $< 0.01$) were selected as primitive biomarkers.

@@

% Cox Risk Regression Establishment and Validation with lncRNA data
%HNSCC samples were randomly divided into a training set and a validation set. Univariate Cox regression was used to select prognosis-associated genes (\textit{p} value $< 0.05$). Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
%establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
%https://glmnet.stanford.edu/articles/glmnet.html
%Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation

@@

\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.\\
After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
%NCBI Reference Sequences (RefSeq)
According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
% keyword: (SLC35E2) AND "Homo sapiens" 
SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B, and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
% updated on 18-May-2021
\end{outline}

@@

%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
We analysed GSE2837 dataset (NCBI GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.

>>>>

%%% for abbreviations, or acronyms
\usepackage[automake, acronym, nopostdot]{glossaries} 
%\usepackage{glossary-inline}
%\newenvironment{abbreviation}
%\makeglossaries %https://tex.stackexchange.com/questions/110095/list-of-acronyms-is-not-displayed
\newacronym{ncbi}{NCBI}{National Center for Biotechnology Information}
\newacronym{degs}{DEGs}{differentially expressed genes}

@@

\subsection*{1-1}
%\begin{MyColorPar}{blue}
%(OK)
First of all, please describe the difference between the two manuscripts.

@@

\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comments and thanks for the agreement with our analysis using the TCGA cohort.

@@

\subsection*{1-2}
\label{page:1-2}
% (OK)
Half of the discussion part was occupied with holistic and spiritual influence on patient’s survival.
The latter half of the discussion may not be appropriate for this manuscript. Many people aware of the relationship between prognosis and mental/financial/familial situations. Unfortunately, almost all authors do not understand why half of the discussion part was occupied with spiritual something. Isn’t it a totally different theme from biomarkers of HNSCC?
Stress may affect the expression level of these biomarkers, which may result in an unexpected prognosis, the main theme of this manuscript is different. If you want to describe spiritual something, please submit it as a brand new manuscript.
Please remember my opinion does not intend to insult your religion because I am also a Buddhist and morning meditation always allow me to start a wonderful day.

@@

\begin{MyColorPar}{blue}
Answer
%(OK)
After morning meditation in a wonderful day of February 2021,, the first author (Dr. Chi) has raised this idea then wrote it in discussion section with comprehensive references. Dr. Chi want to express that "Stress should also be a kind of biomarker included in the future HNSCC study".
We appreciate the reviewer for the agreement about mindfulness meditation and holistic cancer care. We will brief this issue and move rest of it in the other manuscript.

@@

The authors introduced a workflow to identify gene-expression biomarkers based on TCGA data and applied it to head and neck squamous cell carcinoma. The authors tried to highlight their workflow and present it as a new tool, however, their workflow is very common, and I cannot see its novelty. 
The selection of gene expression cutoff is not well handled statistically (see below my first comment). % FDR
Therefore, I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone
Exploring all possible expression cutoffs is also usable but should only be used for established biomarkers. Once it is known that a gene is a strong biomarker (e.g., from a genome-wide test using fixed cutoffs), one can fine-tune the cutoffs utilizing this strategy.

\subsection*{2-1}%(ok)
% sliding window cutoff selection with FDR corrected
Exploring all possible expression cutoffs is controversial. 
A robust expression biomarker should be effective and detectable at most major cutoffs. Compared to a fixed quantile cutoff, a sliding window cutoff selection of cutoffs would capture more genes whose p-values just reach the significant level (p=0.05). 
For example, a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 0.04 at 70\% quantile cutoff. % might be false positive
But it is not expected that a gene with a p-value of 0.1 at 25\% or 50\% quantile cutoff could achieve a p-value of 1e-5 at 70\% quantile cutoff. % true positive
This strategy only identifies more weak “biomarkers,” and it also captures more false positives. 
Adjustment of multiple test p-values should be applied here, which is missing in the current manuscript.
% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity

%
\begin{MyColorPar}{blue}
Answer
%(ok)

% 1) ***We modified the workflow as ...(本來就有計算 FDR and excluding >= 0.05)
% 2) and FDR (done)
We appreciate the reviewer to kindly advise us about the principle of sliding window cutoff selection in detail.
% and give us this nomenclature as "sliding window"
We correct our statement of this workflow (please see Answer 2-2).
There is more evidence to validate them (please see Answer 2-3).

%\begin{MyColorPar}{red}
%\end{MyColorPar}

% and FDR (done; ok)
We also modified the last paragraph of "Cutoff Finder Core Engine" in the Material and Methods section.
%Figure 1, Table 1, 2 correction: Kaplan-Meier FDR correction
The caption of Figure 1, Table 1, and Table 2 has description about 1) FDR correction of Kaplan-Meier \textit{P} values during Cutoff finding; and 2) Bonferroni correction of Kaplan-Meier \textit{P} values after Cox modeling for candidate selection.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

\begin{MyColorPar}{red}
% TCGA_HNSCC_marginSFP.R [line 111] cutoffReturn <- cutofFinder_func_HNSCC.R
% retrieving optimized (minimal) p value of each Kaplan-Meier plot 
% **A summary table of P-value, Z-score standardization from all HNSCC_survival*.Rda 
% 不必每次重 run (saved at HNSCC_OS_marginS_pvalueKM_candidate_cox.Rda)
% variable name: candidate_sample (with gene symbol and KM p value), candidate_cox, n_percent_Bonferroni
%=> FDR() or p.adjust() The FDR function uses the Benjamini & Hochberg (\cite{Benjamini1995a}) ("BH", alias "fdr") correction by default.
% analysis_export.R [line 197] has FDR < 0.05 for filtering (done)
% [line 196] OS_pvalueS$p_value_adj_FDR <- p.adjust(OS_pvalue$p_OS, method='fdr')

% (stored at HNSCC_survivalAnalysis_marginS_[gene].Rda; file20500_list.txt)
The \acrfull{fdr} ($< 0.05$) correction\cite{Benjamini1995a} has been be applied and shows which genes should be retained for further univariate and multivariate analysis.
% of Cox modeling
It is ensure the control of type I error of multiple test \textit{P} values during our cutoff finding procedure.
\end{MyColorPar}

@@

\subsection*{2-2}
%(OK)
I recommend the authors weaken their statement of the workflow but focus on the identified biomarkers in neck squamous cell carcinoma and use as much as possible evidence to support or validate them. % new Title, abstract, change tone

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment.
We changed title as "Transcriptomics Analysis of Expressions of Ten genes and Their Prognostic Value in Head and Neck Squamous Cell Carcinoma", and abstract; we also changed the tone in our manuscript to focus on the identified biomarkers in the head and neck squamous cell carcinoma.
There is more evidence to validate them (please see Answer 2-3).

\subsection*{2-3}
% PPV positive prediction value => prevalence-sensitive (COVID-19 盛行率的觀念一致) ROC from sensitivity and specificity
% strategy should changing; run GCP Rstudio? hard work to do
In the independent test, half genes have p-values less than 0.05, and most of them have p-values $> 0.01$. % table 1
Purely based on the number of genes and their p-values, the validation rate is relatively low, and the usability of the biomarkers is questionable. % the validation rate 
The p-values are affected by the sample size, which should be described in the main text. % writing
As I mentioned above, the authors should look for more data to verify these biomarkers. % GEO

@@

% the validation rate
% more GSE datasets
% using  receiver operating characteristic (ROC) analysis and more GEO datasets
We appreciate the reviewer for the critical comments and thanks for the agreement of our work in cancer research.

%***調整 workflow 更加嚴格以增加 validation rate
Validation rate:\\
%重新挑選 candidate (from Cox) 多選一些、偷偷看答案(GSE2837 and GSE65858)

@@

Validation by:
%TCIA CPTAC (not HPA 抗體很少）

This collection contains subjects from the National Cancer Institute’s Clinical Proteomic Tumor Analysis Consortium Head-and-Neck cancer (CPTAC-HNSCC) cohort.
%https://wiki.cancerimagingarchive.net/display/Public/CPTAC-HNSCC
As digital tissue microarray?

%%%
For validation by GEO datasets:

% National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009)

GEOquery\cite{Sean2007}: SOFT file (or MINiML)
the NCBI GEO repositories
%https://warwick.ac.uk/fac/sci/moac/people/students/peter_cock/r/geo/
*the authors should look for more data to verify these biomarkers.
by TMA IHC of HNSCC (provided by Prof. Michael Hsiao)
or CPTAC (digital TMA, not HPA)i

or more GEO datasets (*GEO2837, GSE40774, ***GSE65858, *GSE117973, GSE148944, and GSE41613/xGSE42743)
* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837

*** https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE65858 GSE65858
https://onlinelibrary.wiley.com/doi/full/10.1002/ijc.29649
OS event and RFS event and survival time
n=270\cite{Wichmann2015}
Each array on the HumanHT-12 v4 Expression BeadChip targets more than 31,000 annotated genes with more than 47,000 probes derived from the \acrfull{ncbi} Reference Sequence (RefSeq) Release 38 (November 7, 2009) and other sources.
% https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GPL10558

**  (GSE117973) Patients of the Heidelberg Center for Personalized Oncology-Head and Neck Cancer (HIPO-HNC) cohort (n = 87, GSE117973) were treated between 2012 and 2016 at the University Hospital Heidelberg, Germany.
PFS and DSS event and months

*x* \cite{Zhao2018} used GSE41613 (with survival data of 97 HNSCC cohort) for DEGs.
GEO2R: GSE41613 and GSE42743 可是*** has only 131 genes of the Affymetrix array data % https://www.ncbi.nlm.nih.gov/geo/geo2r/?acc=GSE41613
from 97 HPV-negative OSCC patients %on the 131 gene 
to identify a model for prediction of OSCC-specific survival\cite{Lohavanichbutr2013}.

x 7. Integration of molecular gene signatures with clinicopathological variables improves staging and outcome prediction of oral cancer.
(Submitter supplied) The aim of this study is to identify and validate clinically implementable gene signatures for outcome prediction of patients with oral squamous cell carcinoma.
Organism:	Homo sapiens
Type:		Expression profiling by array
Platform: GPL6480 99 Samples
FTP download: GEO (TXT) ftp://ftp.ncbi.nlm.nih.gov/geo/series/GSE84nnn/GSE84846/
Series		Accession: GSE84846	ID: 200084846
only alive or death (no survival time) => Similarly preprocessed VUmc (GSE84846) and UMCU (GSE30788) microarray datasets (https://www.oncotarget.com/article/19576/text/)
\cite{Mes2017}

%as following: % search by StarGEO ===========
StarGEO http://stargeo.org/ searching: HNSCC + survival (n>100]
* GSE2837 https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837

x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE40774
n=134; Agilent-026652 Whole Human Genome Microarray 4x44K v2 (Probe Name version)
supplementary data:
https://clincancerres.aacrjournals.org/content/21/4/870.figures-only#fig-data-additional-files
n=134 (no survival)
# Version info: R 3.2.3, Biobase 2.30.0, GEOquery 2.40.0, limma getGEO("GSE40774", GSEMatrix =TRUE, cex=1.5)library("maptools")

x https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE148944
   784 probes (gene）
n=40; 110 FFPE samples were collected from a retrospective cohort of 67 OTSCC patients and 10 non-cancerous tongue samples. Targets including CD4, CD8, FOXP3, PD-L1 and PD-1 were analyzed by immunohistochemistry. The Nanostring PanCancer Immune Profiling Panel was used for gene expression profiling. Data were externally validated in the TCGA head and neck (HNSCC), melanoma and lung squamous cell carcinoma (LSCC) cohorts.
GPL28285 NanoString nCounter PanCancer Immune Profiling Panel

@@

% *** how to do? ROC
% https://compgenomr.github.io/book/assessing-the-performance-of-our-model.html
In addition, receiver operating characteristic (ROC) analysis was used to estimate the predictive power of this signature\cite{Huang2019}.
%---

We also modified the last paragraph in the Material and Methods section, and also described "the p-values are affected by the sample size" in the Discussion section.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

\begin{MyColorPar}{red}
validation rate
...the \textit{P} value is affected by the sample size. % TCGA has the most HNSCC sample size

\end{MyColorPar} % red

\end{MyColorPar} % blue

% #####################
\subsection*{2-4} % (ok)
%(OK)
How univariable and multivariable tests work should be clearly described in the main text. In a multivariable test, which variables were used?

%
\begin{MyColorPar}{blue}
Answer
%(OK)
We appreciate the reviewer for the critical comment and modified the Materials and Methods accordingly.
The paragraphs marked in \textcolor{red}{Red} from page 2 (line 77) to page 3 (line 129) are the part of the manuscript that has been revised. Also, it was shown here in the following paragraph.
\\[0.3cm]

@@

\subsection*{2-6}
%(OK)
\subsubsection*{[Minor comments]}
The background should be revised extensively. For example, the description of the linear model should be removed. X1...Xn should be removed. 
More introduction to how other researchers used TCGA to find expression biomarkers should be presented. 
Detailed introduction of TCGA-related tools should be removed or moved to Methods.
In line 154 paragraph, what does unclean data mean, missing values or zero expression? The three challenges are not “challenges” at all. The authors exaggerated the difficulties here. 
In Figure 1, the diagram should have direction. 
The file names are not interesting. RNAseq (20500 genes) should be gene expression values (20500 genes)
In Figure 2, unlabeled scales on the x-axis.

%
\begin{MyColorPar}{blue}
Answer
%(OK x3)
% (ok) minor comments1
We appreciate the reviewer for the critical comments and thanks for the agreement of our workflow in cancer research.
The description of the linear model has been removed. 
Detailed introduction of TCGA-related tools has been moved to the Materials and Methods.
We made a new Figure 1 with clear direction of the workflow.
A "gene expression values (20500 genes)" in Figure 1, instead of "RNAseq", indicates the expression data obtained from the TCGA.
In Figure 2, the ticks and labels on the x-axis were corrected.\\[0.5cm]

@@

Xu and his collegues\cite{Xu2021a} also used Kaplan–Meier survival curves along with a log-rank test or univariate Cox regression to screen prognostic factors (\textit{P} value $< 0.05$), and those prognostic factors whose expression levels were significantly relevant to patients' overall survival (\textit{P} value $< 0.01$) were selected as primitive biomarkers.

@@

% Cox Risk Regression Establishment and Validation with lncRNA data
%HNSCC samples were randomly divided into a training set and a validation set. Univariate Cox regression was used to select prognosis-associated genes (\textit{P} value $< 0.05$). Subsequently, we performed "Least Absolute Shrinkage and Selection Operator" (LASSO) Cox regression model to do feature selection\cite{Tibshirani1996};
%establish a prognostic risk score model, and the penalty regularization parameter lambda ($\lambda$) was chosen through cross-validation with an n-fold equal to 10 by using the R package glmnet (21). 
%https://glmnet.stanford.edu/articles/glmnet.html
%Lambda.min was identified to pick out the variables. According to these variables, a stepwise regression was performed to establish the Cox model. 
%Least Absolute Shrinkage and Selection Operator (LASSO) cox regression model along with 10-fold cross-validation

@@

\1 Updated number of protein-coding genes in the TCGA HNSCC is 20500.\\
After investigation of mRNA expression dataset obtained through NCI's Firehose API, we found that gene ID (9906), gene ID (728661), and their expression values were saved together under the entity of gene symbol "SLC35E2".
The expression file of SLC35E2 has almost double in size than those of SLC35E1 or SLC35E3.
% http://gepia2.cancer-pku.cn/#survival is SLC35E2; 證明 TCGA has error
% [line 1549]
%HNSCC.mRNA.Exp.SLC35E2.Fire.Rda
%[line 1654]
%for gene correction (20499 to 20500) from SLC35E2 to 2 genes:
%NCBI Reference Sequences (RefSeq) National Center for Biotechnology Information Reference Sequence (NCBI) RefSeq Release 38 (November 7, 2009) 
According to the Human Gene Database (available at https://www.genecards.org/Search\\/Keyword?queryString=SLC35E2), SLC35E2A (Gene ID: 9906) and\\ SLC35E2B (Gene ID: 728661) should be the correct entities for TCGA HNSCC dataset.
% https://www.ncbi.nlm.nih.gov/gene/?term=(SLC35E2)+AND+%22Homo+sapiens%22
% keyword: (SLC35E2) AND "Homo sapiens" 
SLC35E2 is the previous symbol of SLC35E2A (reference at https://www.genenames.org/data/gene-symbol-report/\#!\\/hgnc\_id/HGNC:20863).
Thus, we made reassignment of the expression value of SLC35E2A and SLC35E2B, and updated the number of protein-coding genes in the TCGA HNSCC from 20499 to 20500.
% updated on 18-May-2021
\end{outline}

@@

%\subsubsection*{GSE2837} % non-TCGA
% from Anwser2-2
%by GEO GSE2837 HNSCC dataset (PrognoScan)
We analysed GSE2837 dataset (\acrfull{ncbi} GEO database\cite{Chung2006}, HNSCC cohort has 28 participants) from online tools: PrognoScan (availalbe at http://dna00.\\bio.kyutech.ac.jp/PrognoScan/)\cite{Mizuno2009a}.
%??MD Anderson (40 cases) SurvNet: https://bioinformatics.mdanderson.org/SurvNet/
%https://www.ncbi.nlm.nih.gov/geo/query/acc.cgi?acc=GSE2837 \cite{Chung2006}
The GSE2837 carries % VUMC, VAMC, UTMDACC (1992-2005)
relapse-free survival (RFS) data, instead of overall survival in TCGA dataset,
and microarray gene expression (by Affymetrix X3P chips U133\_X3P).
The survival significance (Kaplan Meier P-value) is in the following probes of 10 genes:\\
1) poor prognosis: CAMK2N1 (0.048214), PGK1 (0.009978), SURF4 (0.023127), USP10 (0.017768), NDFIP1 (0.022758), FOXA2 (0.001587); % FOXA2 (0.038125)
2) better prognosis: IL19 (0.049731), FCGBP (0.005658), KIAA1683 (IQCN, 0.005886), NPB (0.014177);
%17 out of 20 candidates
%?DKK1 (0.253635), 
Please see Supplementary Figure S3. %\ref{figure:fig_GSE2837}.
Nevertheless, PrognoScan has group separation cut by a skewed manner, and the GSE2837 has far fewer participants than the TCGA cohort.
%DKK1, CAMK2N1, STC2, PGK1, SURF4, USP10, NDFIP1, FOXA2, STIP1, DKC1;
%ZNF557, ZNF266, IL19, MYO1H, FCGBP, LOC148709, EVPLL, PNMA5, KIAA1683 (IQCN), NPB
%Those 11 genes achieve similar positive and negative prognostic effect comparable with our proposed candidate genes. 
The 10 out of 20 positive and negative prognostic genes underlined is confirmed by comparable studies using the GSE2837 dataset other than the TCGA cohort.
